Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-17 jss/article.tex
[skip ci] jss update

We can now plot the first ten rows of the results obtained for corrected and uncorrected fisher test with heatmap format (Figure~\ref{fig:heatm}) or barplot (Figure~\ref{fig:barp}).

>>>>

We can now plot the first ten rows of the results obtained for corrected and
uncorrected fisher test with heatmap format (Figure~\ref{fig:heatm}) or barplot
(Figure~\ref{fig:barp}) with the following commands:

\begin{verbatim}
# heatmap

represent_enrichment(enrichment = list(SampleA = enrichment_test[1:10,], 
  SampleB = enrichment_test[3:10,]), plot = "heatmap", scale = "log", 
  low = "steelblue" , high ="white", na.value = "grey")

# barplot

represent_enrichment(enrichment = list(SampleA = enrichment_test[1:10,],
 SampleB = enrichment_test[3:10,]), plot = "bar", scale = "log", nrow = 1)
\end{verbatim}
